Constraining Quiescent Supermassive Black Hole Environments.

### 2014-09-01 ms.tex
Some changes to intro.

In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.  The accretion rate in turn has implications for rate of black hole growth. 
%AG:Perhaps need more detail here.

@@

The gas in the vicinity of a black hole may come from several sources. \citealt{Ho:2009a} proposes three different mechanisms (1) Mass loss in winds (particularly from evolved stars) (2) Stellar-stellar collisions in dense environments (3) Tidal disruptions of stars. To estimate (a lower limit on the accretion rate), \citealt{Ho:2009a} calculates the Bondi accretion rate based on typical observed gas densities and temperatures taken from Chandra X-ray observations. A second estimate is obtained from the wind mass loss rate from the observed stellar densities. Both of the estimates suggest that there is an ample reservoir of gas to power active galactic nuclei in quiescent galaxies. This suggests that the lack of the AGN activity is due to the fact that the the accretion proceeds in a radiatively inefficient mode.

@@

 %%AG--say something about x-ray observations.

>>>>

In order to understand why most galaxies appear to be inactive, it is necessary to understand the gas environment of black holes, as the gas density around the black hole sets its accretion rate.  The accretion rate also has implications for rate of black hole growth. 
%AG:Perhaps need more detail here.

@@

The gas in the vicinity of a black hole may come from several sources. \citealt{Ho:2009a} proposes three different mechanisms (1) Mass loss in winds (particularly from evolved stars) (2) Stellar-stellar collisions in dense environments (3) Tidal disruptions of stars. To estimate (a lower limit on the accretion rate), \citealt{Ho:2009a} calculates the Bondi accretion rate based on typical observed gas densities and temperatures taken from Chandra X-ray observations. A second estimate is obtained from the wind mass loss rate from the observed stellar densities. Both of the estimates suggest that there is an ample reservoir of gas to power active galactic nuclei in quiescent galaxies. This suggests that the lack of the AGN activity is due to the fact that the accretion proceeds in a radiatively inefficient mode.

@@

We compare our calculated gas profiles to those inferred from Chandra X-ray observations by \citealt{AllenDunn+:2006a} and \citealt{RussellMcNamara+:2013a}. Additionally, we chack how well our results are able to reproduced relationships between $L_x$ and $\Mbh$. In performing these comparisons we hope to determine how well the gas environments of quiescent galaxies may be understood using the relatively well understood physics of stellar winds and supernova heating.
 %%AG--say something about x-ray observations.
